---
title: "projectutils"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R package aims to make it easier to coordinate CorrelAid projects by providing utility functions. 
Additional, more text-focused help can be found in the [documentation for project coordinators](https://docs.correlaid.org/project-manual/project-coordinators).

## Installation
This package is only available on GitHub and there are no plans to submit it to CRAN.

with `{devtools}` :package:
```{r eval=FALSE}
devtools::install_github("CorrelAid/projectutils")
```

or with the `{remotes}` :package: 
```{r eval=FALSE}
remotes::install_github("CorrelAid/projectutils")
```


#### Create new projects data

#### Download applications for your project 


Please see the README of the [`surveymonkey`](https://github.com/tntp/surveymonkey#add-your-oauth-token-to-your-rprofile) package on how to make this token accessible to your R session.


```{r}
library(projectutils)
test <- load_project_applications("TES-2020-02")
```