---
params:
  applicant_id: 1
  anon_path: "data/applications_anonymized.csv"
output: rmdformats::robobook
---
<!-- THIS FILE IS NOT SUPPOSED TO BE KNITTED BY HAND
    INSTEAD IT IS KNIT AUTOMATICALLY 
    BY THE APPLICATIONS_REPORT.RMD FILE FOR EACH APPLICANT.
    YOU CAN EDIT THIS FILE IF YOU WANT TO CHANGE THE INFORMATION DISPLAYED FOR EACH APPLICANT
-->
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(readr)
library(stringr)

lvls <- tibble(level_num = c(0, 1, 2, 3), level = c("beginner", "user", "advanced", "expert"))
# theme and palette
theme_set(correltools::theme_correlaid(base_size = 12))
correlpal <- correltools::correlaid_pal()
```

```{r message=FALSE}
appl <- readr::read_csv(params$anon_path, col_types = cols())

a <- appl %>% 
  filter(applicant_id == params$applicant_id) 

if (nrow(a) == 0) stop(glue::glue('There is no applicant with id {params$applicant_id}. Available ids: {paste(appl$applicant_id, collapse = ", ")}'))

gender_str <- stringr::str_replace(a$gender, '_', ' ')
role_str <- stringr::str_replace(a$project_role, '_', ' ')

a_skills <- a %>% 
  select(applicant_id, starts_with(c("skills", "techniques", "topics"))) %>% 
  pivot_longer(starts_with(c("skills", "techniques", "topics")), names_to = "category", values_to = "level") %>% 
  mutate(question = stringr::str_extract(category, "skills|techniques|topics")) %>% 
  mutate(category = stringr::str_replace(category, "skills_|techniques_|topics_", "")) %>% 
  mutate(category = stringr::str_replace_all(category, '_', ' ')) %>% 
  rownames_to_column() %>% 
  left_join(lvls, by = "level")
```

# `r a$applicant_id` - `r gender_str` - `r role_str` {#applicant-`r a$applicant_id`}
**Gender**: `r gender_str`

**Project role for this project**: `r role_str`
 
**Projects they applied to**: `r a$applied_to %>% stringr::str_replace_all(' ', ', ')`

**German skills**: `r a$german_skills`

### Past applications
```{r results='asis'}
if (is.na(a$past_applications)) {
  cat('No information about past applications was collected')
}

if (a$past_applications == 'first_application') {
  cat('The applicant is applying to a CorrelAid project for the **first time**.')
} else if(a$past_applications == 'successful') {
    cat(glue::glue('The applicant has **successfully applied** to a CorrelAid project before.'))
} else if(a$past_applications == 'not_successful') {
    cat(glue::glue("The applicant was **not successful** with their application(s) so far. They specified the following when asked about when/where they have applied in the past:\n\n > {a$past_applications_details}"))
}
```

### What skills qualify you?

`r a$motivation_skills`

### Why do you want to get involved?

`r a$motivation_why_involved`

### Self-rated experience with skills, techniques and topics 

```{r fig.height=8, fig.width=6}
ggplot(a_skills, aes(x = category, y = level_num, group = question)) +
  geom_segment(aes(
    x = fct_rev(category),
    xend = fct_rev(category),
    y = 0,
    yend = level_num
  )) +
  geom_point(size = 3, color = correlpal(1)) +
  coord_flip() +
  theme(
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none"
  ) +
  scale_y_continuous(
    "level",
    limits = c(0, max(lvls$level_num)),
    breaks = seq(0, max(lvls$level_num), 1),
    labels = lvls$level
  ) +
  facet_wrap(~question, nrow = 3, scales = "free_y") +
  xlab("")
```


